Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy

### 2017-09-02 paper/paper.tex
latest paper

A larger dynamical mass estimate over its baryonic mass is a hint that
\tol\ is dark matter dominated.  
Following the methodology of \citet{2011ApJ...726..108T} we estimate
that a dark matter halo with a virial mass $\sim 6\times 10^{11}$
M$_{\odot}$ {\bf and a virial radius $220$ kpc } could explain this dynamical mass.
This estimate is based on computing the integrated mass profile of a
spherical dark matter halo with a Navarro-Frenk-White profile with its
concentration following the median mass-concentration
relationship found in the Bolshoi simulation
\citep{2012MNRAS.423.3018P,2016ApJ...832..169P}.  
Figure \ref{fig:mass} shows the enclosed mass as a function of radius
for different dark matter halos together with the \tol's dynamical
mass estimate. 
{\bf This value should be considered an upper bound as lower values
  could be achieved if one considers instead a cored profile.}
{\bf More realistic mass estimates can only achieved by detailed mass
  modelling once \tol's full rotation curve   becomes available.}

>>>>

A larger dynamical mass estimate over its baryonic mass is a hint that
\tol\ is dark matter dominated.  
Following the methodology of \citet{2011ApJ...726..108T} we estimate
that a dark matter halo with a virial mass $\sim 6\times 10^{11}$
M$_{\odot}$ {\bf and a virial radius $220$ kpc } could explain this dynamical mass.
This estimate is based on computing the integrated mass profile of a
spherical dark matter halo with a Navarro-Frenk-White profile with its
concentration following the median mass-concentration
relationship found in the Bolshoi simulation
\citep{2012MNRAS.423.3018P,2016ApJ...832..169P}.  
Figure \ref{fig:mass} shows the enclosed mass as a function of radius
for different dark matter halos together with the \tol's dynamical
mass estimate. 
{\bf This should be considered an an upper bound as lower values
  could be achieved if one considers instead a cored profile.}
{\bf Realistic mass estimates could only be achieved by detailed mass
  modelling once \tol's full rotation curve   becomes available.}
